Automated Formal Synthesis of Optimal Sizing for Stand-alone Solar Photovoltaic Systems\\

### 2019-05-04 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
updated title
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
updated ASE text double-blind

\title{Synthesizing Optimal Sizing of Stand-alone Solar Photovoltaic Systems\\
% \thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{Alessandro Trindade}
\IEEEauthorblockA{
\textit{Federal University of Amazonas}, Brazil \\
alessandrotrindade@ufam.edu.br}
\and
\IEEEauthorblockN{Lucas Cordeiro}
\IEEEauthorblockA{
\textit{University of Manchester}, UK \\
lucas.cordeiro@manchester.ac.uk }
}

\maketitle

@@

%\begin{IEEEkeywords}
%automated verification, model checking, program synthesis, electrical systems, and solar photovoltaic systems.
%\end{IEEEkeywords}

@@

	\STATE Requeriment enforced by \textbf{assume}$(V_{c})$ \\

@@

%	\STATE Requeriment enforced by \textbf{assume}$(V_{in}DC \wedge V_{out}AC )$ \\
%	\STATE Requeriment enforced by \textbf{assume}$(V_{out}AC)$ \\

@@

%	\STATE Requeriment enforced by \textbf{assume}$(P_{surge})$ \\

>>>>

\title{Automated Formal Synthesis of Optimal Sizing for Stand-alone Solar Photovoltaic Systems\\
% \thanks{Identify applicable funding agency here. If none, delete this.}
}
%
%\author{\IEEEauthorblockN{Alessandro Trindade}
%\IEEEauthorblockA{
%\textit{Federal University of Amazonas}, Brazil \\
%alessandrotrindade@ufam.edu.br}
%\and
%\IEEEauthorblockN{Lucas Cordeiro}
%\IEEEauthorblockA{
%\textit{University of Manchester}, UK \\
%lucas.cordeiro@manchester.ac.uk }
%}
%
\maketitle

@@

\begin{IEEEkeywords}
automated verification, model checking, program synthesis, electrical systems, and solar photovoltaic systems.
\end{IEEEkeywords}

@@

	\STATE Requirement enforced by \textbf{assume}$(V_{c})$ \\

@@

%	\STATE Requirement enforced by \textbf{assume}$(V_{in}DC \wedge V_{out}AC )$ \\
%	\STATE Requirement enforced by \textbf{assume}$(V_{out}AC)$ \\

@@

%	\STATE Requirement enforced by \textbf{assume}$(P_{surge})$ \\
